The Topic Browser\\An Interactive Tool for Browsing Topic Models

### 2010-10-28 masters_thesis/browser_nips/paper.tex
A couple of minor changes to the browser paper

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
Matthew J. Gardner \\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
\And
Joshua Lutes \\
Department of Computer Science \\
Brigham Young University \\
\texttt{joshua@byu.edu} \\
\And
Jeff Lund \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jefflund@gmail.com} \\
\And
Josh Hansen \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jjfresh@byu.edu} \\
\And
Dan Walker \\
Department of Computer Science \\
Brigham Young University \\
\texttt{danwalkeriv@gmail.com} \\
\And
Eric Ringger \\
Department of Computer Science \\
Brigham Young University \\
\texttt{ringger@cs.byu.edu} \\
\And
Kevin Seppi \\
Department of Computer Science \\
Brigham Young University \\
\texttt{kseppi@cs.byu.edu} \\
}

@@

We have presented the Topic Browser, an interactive tool for browsing both the
output of a topic model and the corpus that was modeled.  We have shown that
our tool incorporates many previously published visualizations of topic models,
including basic corpus browsing functionality, plots of trends over attributes
in the corpus, and Blei \& Lafferty's Turbo Topics method of finding
significant phrases for each topic.  We have also presented many novel ways to
mine information from a topical analysis of a corpus in an interactive browsing
experience.  The Topic Browser is an effective tool both for those wishing to
browse through a corpus in the context of a topic model, and for those wishing
to better understand topic models and develop new models.

>>>>

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
Matthew J. Gardner \\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
\And
Joshua Lutes \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jlutes@byu.edu} \\
\And
Jeff Lund \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jefflund@gmail.com} \\
\And
Josh Hansen \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jjfresh@byu.edu} \\
\And
Dan Walker \\
Department of Computer Science \\
Brigham Young University \\
\texttt{danwalkeriv@gmail.com} \\
\And
Eric Ringger \\
Department of Computer Science \\
Brigham Young University \\
\texttt{ringger@cs.byu.edu} \\
\And
Kevin Seppi \\
Department of Computer Science \\
Brigham Young University \\
\texttt{kseppi@cs.byu.edu} \\
}

@@

We have presented the Topic Browser, an interactive tool for browsing both the
output of a topic model and the corpus that was modeled.  We have shown that
our tool incorporates many previously published visualizations of topic models,
including basic corpus browsing functionality, plots of trends over attributes
in the corpus, the use of coherence to ignore meaningless topics, and Blei \&
Lafferty's Turbo Topics method of finding significant phrases for each topic.
We have also presented many novel ways to mine information from a topical
analysis of a corpus in an interactive browsing experience.  The Topic Browser
is an effective tool both for those wishing to browse through a corpus in the
context of a topic model, and for those wishing to better understand topic
models and develop new models.
